---
title: "Code Along - Data Viz"
output: html_document
date: "2023-10-12"
---

```{r, echo=FALSE}
htmltools::img(src = knitr::image_uri(file.path("figures/immerse_hex.png")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px;',
               width ="250",
               height ="193")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE,
                      message = FALSE,
                      tidy.opts=list(width.cutoff=60)) #Here, I have made it so that when you knit your .rmd, warnings and messages will not show up in the html markdown. 
```

Load packages

```{r, cache = FALSE}

library(tidyverse)
library(haven)
library(glue)
library(MplusAutomation)
library(here)
library(janitor)
library(gt)
library(cowplot)
library(DiagrammeR) 
library(psych)
here::i_am("lca_viz.Rmd")
```

------------------------------------------------------------------------

### Probability Plots

Read in select model:

```{r}
model <- readModels(here("enum", "c3_bully.out"))
```


Automatic:


```{r fig.height=6, fig.width=10}
source("plot_lca.txt")

plot_lca(model_name = model)
```

------------------------------------------------------------------------

##### Customize Line Plot

Title: Bullying Probability Plot

Class Labels:
  1. Reported Harrassment (Low), Staff (High)
  2. Reported Harrassment (High), Staff (Low)
  3. Reported Harrassment (Low), Staff (Low)
  
Item Labels:
  1. Harassment: Disability
  2. Harassment: Race
  3. Harassment: Sex
  4. School staff: Counselor
  5. School staff: Psychologist
  6  School staff: Law Enforcement


```{r}
#### START EDIT ####

# Read in model. If you have not read in model above, use this code: 
# model <- readModels(here("enum", "c3_bully.out"))

model <- model

# Title (Copy and paste the title above)
title <- ""

# Item labels (C/P the item labels above)
item_labels <- c("","","","","","")

# Class labels (C/P class labels above)
class_labels <- c("", "", "")


#### END EDIT ####
```

Extract data needed for plotting (don't edit):

```{r}
# Extract data needed for plotting (don't edit here)
plot_data <- data.frame(model$parameters$probability.scale) %>% 
  filter(category == 2) %>% 
  mutate(items = fct_inorder(param),
         class = fct_inorder(LatentClass)) %>% 
  mutate(items = factor(items, labels = item_labels),
         class = factor(class, labels = class_labels)) %>% 
  dplyr::select(est, se, class, items)
```


#### Customize Line Plot

```{r}
## Plot data
plot_data %>%
  ggplot(aes( # Specify variable names here
      x = , # Item names
      y = , # Probability values
      group = , # Latent classes (group by latent classes, shape of point, color of line, line type)
      shape = ,
      colour = ,
      lty = 
  )) +
  geom_point(size = 4) +  # Add points to plot
  geom_line() + # Adds line to plot
  ylim(0, 1) + # Adjusts y-axis to include 0-1.
  scale_x_discrete( # This allows the names of the items to wrap around the item labels on the x-axis (remove if you don't need it)
    "",
    labels = function(x)
      str_wrap(x, width = 10)
  ) +
  labs(title = "Figure 1", # Plot labels
       subtitle = title,
       y = "Probability") +
  theme_cowplot() + # Pre-made theme
  scale_color_grey(start = 0, end = .5) +
  # scale_color_manual(values=c('orange', 'pink', 'red')) +
  # scale_shape_manual(values = c(7, 8, 9)) +
  # scale_linetype_manual(values = c("solid","twodashed","dotted")) +
  theme(
    text = element_text(family = "sans", size = 12), # All text elements (except legend)
    legend.text = element_text(family = "sans", size = 12), # Legend text
    legend.key.width = unit(0, "line"), # Removes line from legend symbol
    legend.title = element_blank(), # Removes legend title
    legend.position = "bottom", # Places legend on bottom
    axis.text.x = element_text(vjust = 1),# Vertically adjusts x-axis text
    plot.subtitle = element_text(face = "italic", size = 15), # Italicizes subtitle
    plot.title = element_text(size = 15) # Adjusts plot title size
  )
```

```{r}
ggsave(here("figures", "custom_line_plot.png"), dpi = "retina", bg = "white", height=6, width=9, units="in")
```


Bar Plot:

```{r}
## Plot data
plot_data %>%
  ggplot(
    aes(
      x = items,
      y = est,
      fill = class # Fill is for bar plot
    )
  ) +
  geom_bar(stat = "identity", position = "dodge", color = 'black') + # "dodge" = grouped bars, "identity" = sum of y variable
  geom_errorbar(aes(ymin=est-se, ymax=est+se), # Add error bars
                size=.3,    
                width=.2,
                position=position_dodge(.9)) + # Positions error bars over each bar
  geom_text(aes(label = est),  # Add probability values 
            family = "sans", size = 4,
            position=position_dodge(.9), # Positions text over each bar  
            vjust = -3) + # Change for location of text
  ylim(0,1) +
  scale_x_discrete("", labels = function(x) str_wrap(x, width = 10)) + # Adds string wrap to item names
  labs(title = "Figure 1",
       subtitle = title,
       y = "Probability") +
  # scale_fill_manual(values=c('orange', 'pink', 'red')) +
  scale_fill_grey(start = 0.2, end = .5) +
  theme_cowplot() +
  theme(
    text = element_text(family = "sans", size = 12),
    legend.text = element_text(family = "sans", size = 12),
    legend.title = element_blank(),
    legend.position = "top",    
    axis.text.x = element_text(vjust = 1),
    plot.subtitle = element_text(face = "italic", size = 15),
    plot.title = element_text(size = 15)
  ) #+
  #coord_flip() # Flips bar plot (to the y axis)
```


```{r}
ggsave(here("figures", "custom_bar_plot.png"), dpi="retina", bg = "white", height=6, width=9, units="in")
```



